---
title: "P8105_hw3_gc2942"
output: github_document
---
## Problem 1
```{r,include=FALSE}
library(tidyverse)
library(skimr)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp =0.6,
  out.width = "90%"
) 

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r setup}
library(p8105.datasets)
data("instacart")
data("brfss_smart2010")
library(skimr)
```

1. There are 134 aisles in the data set. Fresh vegetables aisle are the most items order from.
```{r}
instacart %>% 
  janitor::clean_names() %>% 
  group_by(aisle_id) %>% 
  summarize(n_obs = n())
```

```{r}

instacart %>% 
  janitor::clean_names() %>% 
  group_by(aisle) %>% 
  summarize(frequency = n()) %>% 
  mutate(aisle_rank = min_rank(desc(frequency))) %>% 
  filter(aisle_rank == 1)

```


2. Fresh fruit and fresh vegetables are the most popular aisles that people buy.
```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(frequency = n()) %>%
  filter(frequency > 10000)%>%
  arrange(frequency) %>% 
  ggplot(aes(x = abbreviate(aisle,4), y = frequency)) +
  geom_point(aes(color = aisle))+
  labs(title = "number of items ordered in each aisle",
       x = "aisle with more than 10000 items",
       y = "number of items ordered") +
  viridis::scale_color_viridis(
    name ="aisle",
    discrete = TRUE
  )
  
```


3. The most popular items in baking ingredients are light brown sugar,pure baking sodaand cane sugar. The most popular items in dog food care are snack sticks chicken &rice recipe dag treats, organix chicken & brown rice recipe, and small dog biscuits. The most popualar items in packaged vegetable fruits are oganic baby spinach, organic raspberries, and organic blueberries.
```{r}
instacart %>% 
  select(aisle_id,aisle,product_name) %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle,product_name) %>% 
  summarize(number_of_times = n()) %>% 
  mutate(product_rank = min_rank(desc(number_of_times))) %>% 
  filter(product_rank %in% c(1,2,3)) %>% 
  arrange(aisle,product_rank) %>% 
  knitr::kable(digits = 0)
```

4.The mean hour of day for Coffee Ice Cream is highest in Tuesday.The mean hour of day for Pink Lady Apples is highest in Wednesday.
```{r,warning = FALSE}
instacart %>%   
  filter(product_name == c("Coffee Ice Cream","Pink Lady Apples"))%>%     
  group_by(product_name,order_dow) %>%  
  summarize(mean_hour = mean(order_hour_of_day)) %>%  
  mutate(order_dow = order_dow + 1) %>% 
  mutate(order_dow = lubridate::wday(order_dow, label = TRUE)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>% 
  knitr::kable(digits = 2)
```

There are `r nrow(instacart)` and `r ncol(instacart)` in the instacart data. 
The structure of data is shown by `str(instacart)` and gives us a preview of each column. The key variables are `r names(instacart)`. If we want some observations of data set, we can  look at `r skim(instacart)`.

## Problem 2

```{r}
brfss_smart2010 %>% 
  janitor::clean_names() %>%  
  filter(topic =="Overall Health") %>%  
  select(topic,response) %>% 
  mutate(response = forcats::fct_relevel (response, "Poor", "Fair","Good","Very good","Excellent")) %>% 
  arrange(response)
  
```
```{r,warning=FALSE}
brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  select(year,locationabbr,locationdesc) %>% 
  filter(year == c(2002,2010)) %>% 
  group_by(year,locationabbr)
```




